Papers

### 2024-12-17 papers.qmd
update

A. Heiskala, **J. D. Tucker**, P. Choudhary, R. Nedelec, J. Ronkainen, O. Sarala, M. Järvelin, M. J. Sillanpääm, and Sylvain Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, in revision, 2024.

>>>>

A. Heiskala, **J. D. Tucker**, P. Choudhary, R. Nedelec, J. Ronkainen, O. Sarala, M. Järvelin, M. J. Sillanpääm, and Sylvain Sebert, "Timing based clustering of childhood BMI trajectories reveal differential maturational patterns; Study in the Northern Finland Birth Cohorts 1966 and 1986", *International Journal of Obesity*, accepted, 2024.
